2024 US Presidential Election Model

### 2024-10-19 paper/paper.qmd
committ linear model script and model file

library(tidyverse)
library(palmerpenguins)
```

@@

# Data {#sec-data}

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

>>>>

library(tidyverse)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(readr)
library(dplyr)
```

@@

# Data {#sec-data}
```{r}
# Load the cleaned poll data
clean_poll_data <- read_csv("/Users/jamielee/2024_US_Elections/data/02-analysis_data/analysis_data.csv")

# Group by state and candidate, and calculate the average percentage (pct)
state_average <- clean_poll_data |>
  group_by(state, candidate_name) |>
  summarise(avg_pct = mean(pct, na.rm = TRUE)) |>
  pivot_wider(names_from = candidate_name, values_from = avg_pct) |>
  rename(Trump_pct = "Donald Trump", Harris_pct = "Kamala Harris")

# Replace missing values only in the numeric columns (Trump_pct, Harris_pct)
state_average <- state_average |>
  mutate(across(c(Trump_pct, Harris_pct), ~replace_na(., 0)))
```

@@

To predict the election outcome, we will assume that the higher pct in a state between Trump and Harris determines the winner of the election. The difference in pct is used as the predictor for which candidate wins each state.

@@
